Measurement and Analysis of Child Pornography Trafficking on P2P Networks\nocite{Hurley}

### 2013-10-15 Paper_presentation.tex
So close...

\item[\checkmark]

@@

>>>>

@@

\begin{block}{Gnutella unique libraries on specific days}

\begin{figure}[!htb]
\centering
\includegraphics[scale=0.3]{Libraries_specific_day}
\caption{Gnutella unique libraries on specific days}.
\label{fig:Libraries_specific_day}
\end{figure}

\item[\checkmark]GUIDs with a single file are easily aliased with other GUIDs with the same single file.

\item[\checkmark]About 58\% of GUIDs have unique libraries on a
given day of the dataset.

\item[\checkmark]40\% of Gnutella GUIDs that have two or more FOI:
	\begin{itemize}
	\item Over 95\% have unique libraries.
	\end{itemize}

\item[\checkmark]25\% of GUIDs with three or more FOI: 
	\begin{itemize}
	\item Over 99\% have distinct libraries.
	\end{itemize}

\begin{block}{Basicly:}

\item[\checkmark]GUIDs with two or more files in their library had a unique library about 95\% of the time;

\item[\checkmark]GUIDs with three or more files were unique over 99\% of the time.

\begin{block}{These data suggest:}

\item[\checkmark]GUIDs can be treated as uniquely distinguishable when their libraries contain at least two FOI or when are considered all files that they share.

\item[\checkmark] Users are rarely if ever changing their GUID and appearing on the same day with the same library.

\begin{block}{Uniquesses of partial and complete libraries using Jaccard index}

\begin{figure}[!htb]
\centering
\includegraphics[scale=0.3]{Libraries_unique}
\caption{Uniquesses of partial and complete libraries using Jaccard index}.
\label{fig:Libraries_unique}
\end{figure}
